---
title: "Output of Batclassify"
author: "JF Godeau"
date: "`r Sys.setlocale('LC_ALL', 'en_GB.UTF-8'); format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    fig_caption: yes
    self_contained: no
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
#FILE <- file.choose()
DIR <- "/media/jf/Elements/Audiomoth/20180601_Polany/SPHINX"
FILE <- paste(DIR,"Results.csv",sep="/")
require(data.table)
require(lubridate)
require(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
#knitr::opts_knit$set(root.dir=DIR) # ???
# Threshold value of probablilities to discard
Trsh <- 0.69
```

## General info

```{r 'Reformat Date and Time'}
RBC <- read.csv(FILE)
DT.RBC <- data.table(RBC)
DT.RBC[, Date := ymd(substring(DT.RBC$FileName,1,10))]
DT.RBC[, Time := as.character(hms(substring(DT.RBC$FileName,12,19)))]
PER <- max(ymd_hms(DT.RBC$FileName, tz="Europe/Amsterdam")) - min(ymd_hms(DT.RBC$FileName, tz="Europe/Amsterdam"))
PER.h <- round(difftime(max(ymd_hms(DT.RBC$FileName, tz="Europe/Amsterdam")),
                        min(ymd_hms(DT.RBC$FileName, tz="Europe/Amsterdam"))
                        ,units="hours"),1)
DT.num <- data.table(DT.RBC[,5:16], keep.rownames=T)
#DT.num[,Ppyg := NULL] ## !! Remove Ppyg data!!
LogiLine2keep <- apply(DT.num, 1, max) > Trsh
LogiLine2keepNoPyg <- apply(DT.num[,-10], 1, max) > Trsh

TM <- as.POSIXct(DT.RBC$FileName, format="%Y-%m-%d_%H_%M_%S")
TM.TSH <- data.frame(time=TM[LogiLine2keepNoPyg])
TM.TSH$valmax <- apply(DT.num, 1, max)[LogiLine2keepNoPyg]
require(ggplot2)
#ggplot(TM.TSH, aes(time, valmax)) + geom_point()
G1 <- ggplot(data.frame(TM), aes(TM, 0)) +
  geom_point() +
  theme_bw()+
  #  geom_point(data=TM.TSH, aes(time, valmax), col="red",  inherit.aes = F) +
  #  scale_y_continuous(limits=c(min(TM.TSH$valmax), max(TM.TSH$valmax))) +
  geom_histogram(data=TM.TSH, aes(x=time), stat ="bin",  inherit.aes = F, alpha= 0.5, binwidth=1000) +
  #  scale_y_continuous(sec.axis = sec_axis(~., name = "NEW")) +
  scale_x_datetime(date_breaks="2 hours") +
  theme(axis.text.x = element_text(angle = 90, vjust = 1.0, hjust = 1.0))+
  xlab("Time") + ylab("N samples > Threshold")

```

Name of the folder: **`r unique(DT.RBC$FilePath)`**  
Number of files: **`r dim(DT.RBC)[1]`**  
Number of files with at least one probability value above the threshold (defined as `r Trsh`): **`r sum(LogiLine2keep)`**  
Dates recorded for these files: `r paste(unique(DT.RBC$Date), collapse="; ")`  
Time difference between first and last recording: **`r round(PER,1)`** , (= `r PER.h` hours).  

## Distribution of the data in time  
Black dots at y=0 shows the recording period.  

```{r, fig.height=3}
G1
```



## Maximal score obtained for each species
### All species of Batclassify result table

```{r "Global probability for each species"}
MxSp <- sapply(DT.num, max)
#kable(MxSp, caption="General score")
kable(data.frame(t(MxSp)), caption="General score")
```

### Only species with a probability above the threshold (`r Trsh`)  

```{r "Global probability for each species Sup threshold"}
kable(data.frame(t(MxSp[MxSp > Trsh])), caption="Species with p > 0.5")
```


## Number of files where probability is at least above the threshold
### For each species  

```{r 'Select the species, if any, above the threshold for each file'}
CompMax <- cbind(max.col(DT.num[LogiLine2keep,], "first"),
                 max.col(DT.num[LogiLine2keep,], "last"))
Follow <- apply(DT.num[LogiLine2keep,] ,
                1,
                function(x){ord <- order(x, decreasing = T)
                paste(paste(colnames(DT.num)[ord][ x[ord] > Trsh][-1],
                            x[ord][ x[ord] > Trsh][-1]), collapse=" / ")
                })
LogiOneMax <- CompMax[,1] - CompMax[,2] == 0
DFSpMax <- cbind(FileName=as.character(DT.RBC$FileName[LogiLine2keep]),
                 SpeciesMax=names(DT.num)[CompMax[,1]],
                 Prob=apply(DT.num, 1, max)[LogiLine2keep],
                 OtherSp = as.character(Follow))

if(any(!LogiOneMax)){
  Idx <- which(!LogiOneMax)
  if(sum(!LogiOneMax)>1){
    DFSpMax[Idx,2] <- apply(matrix(names(DT.num)[CompMax],
                                   nrow=length(LogiOneMax))[Idx,],
                            1,
                            function(x) paste(x, collapse="-"))
  } else {
    DFSpMax[Idx,2] <- paste(names(DT.num)[CompMax[Idx,]], collapse = "-")
  }
}
DFSpMax <- data.frame(DFSpMax)

kable(sort(table(DFSpMax$SpeciesMax), decreasing = T), col.names = c("Species","N"))
```

### For each species per category of probability  

```{r SepProbCat}
kable(as.data.frame.matrix(table(DFSpMax$SpeciesMax, round(as.numeric(as.character(DFSpMax$Prob)),1))),
      caption="Number of files with each species for probablility categories")

```


## Fully detailed results

```{r 'Final table (PDF or docx)', include=F}


kable(DFSpMax) #If not html output
```


```{r 'Final table', eval=T, include=T, results='asis'}
suppressPackageStartupMessages(library(googleVis))
require(googleVis)
op <- options(gvis.plot.tag='chart') ### to export the chart/table in knitted html
Table <- gvisTable(DFSpMax)
plot(Table)
```

## Analyse of NSL group

```{r "NSL-metrics"}
require(bioacoustics)
require(ggpubr)
Nms <- DFSpMax$FileName[grepl("NSL", DFSpMax$SpeciesMax) | grepl("NSL", DFSpMax$OtherSp)]
#Nms <- DFSpMax$FileName[grepl("Ppyg", DFSpMax$SpeciesMax) | grepl("Ppyg", DFSpMax$OtherSp)]

Pk <- do.call("rbind",
              lapply(Nms, function(x){
  AUD <- read_audio(paste0(DIR,"/",x,".wav"))
  Output <- try(threshold_detection(AUD,
                                    settings=T, HPF=17000,
                                    FFT_size = 1024, threshold = 6))
  Output$event_data[,c("filename", "starting_time", "duration",
                       "freq_max_amp", "freq_max", "freq_min",
                       "bandwidth", "slope", "curve_neg", "snr")]
}))

## Logicals
Cd.NYCNOC <- Pk$freq_max_amp < 22000 & Pk$freq_min < 21000
Cd.QFC <- Pk$duration > 5 & Pk$bandwidth < 5000


DF.NSL <- data.frame(N.Signals = table(factor(Pk$filename)),
           N.Sig_QFC = as.vector(table(Pk$filename[Cd.QFC])),
           N.Sig_NYCNOC = as.vector(table(Pk$filename[Cd.NYCNOC])))
kable(DF.NSL[order(DF.NSL$N.Signals.Freq, decreasing = T),])

```

The samples evaluated with at least 70% of probablility of belonging to the *NSL group* are analyzed broadly.  
`r length(levels(Pk$filename))` files are selected, totalizing `r dim(Pk)[1]` signals.  

### Full dataset of NSL
#### Dispersion on the FME and FT scale.  


```{r "NSL-plot1"}
theme_set(theme_bw())

## Plots
Gx1 <- ggplot(Pk, aes(y=freq_max_amp, x=factor(1))) +
  geom_boxplot() + geom_jitter(aes(color=filename, alpha = 0.4)) +
  ggtitle("FME (limit Nnoc ~ 22 kHz)") +
  geom_hline(yintercept = 22000, color='red', linetype=2) +
  xlab("")
Gx2 <- ggplot(Pk, aes(y=freq_min, x=factor(1))) +
  geom_boxplot() + geom_jitter(aes(color=filename, alpha = 0.3)) +
  ggtitle("FT (limit Nnoc ~ 21 kHz)") +
  geom_hline(yintercept = 21000, color='orange', linetype=2) +
  xlab("")
ggarrange(Gx1, Gx2, legend = 'none')

```

#### Plots *Barataud*

```{r "NSL-plot2"}
G1 <- ggplot(data=Pk, aes(x=freq_max_amp, y=bandwidth, color=filename)) +
  geom_point() + ggtitle("LB vs. FME")
G2 <- ggplot(data=Pk, aes(x=duration, y=freq_min, color=filename)) +
  geom_point() + ggtitle("FT vs. Durée")
ggarrange(G1, G2, common.legend = T, legend = 'none')
```

### Selection of possible QFC
i.e. duration > 5 ms and LB < 5 kHz

```{r "NSL-plot3"}
qfc.y1 <- c(0,6000)
qfc.x1 <- c(15000,36000)
qfc.y2 <- c(15000,36000)
qfc.x2 <- c(5,26)


table(factor(Pk$filename[Cd.QFC]))

Gqfc1 <- ggplot(data=Pk[Cd.QFC,], aes(x=freq_max_amp, y=bandwidth, color=filename)) +
  geom_point()  + ggtitle("LB vs. FME (QFC only!)") + ylim(qfc.y1) + xlim(qfc.x1)
Gqfc2 <- ggplot(data=Pk[Cd.QFC,], aes(x=duration, y=freq_min, color=filename)) +
  geom_point()  + ggtitle("FT vs. Durée (QFC only!)") + ylim(qfc.y2) + xlim(qfc.x2)
ggarrange(Gqfc1, Gqfc2, common.legend = T, legend = 'none')

```

### Selection of possible *Nyctalus noctula*
i. e. FME < 22 kHz and FT < 21 kHz

```{r "NSL-plot4"}
table(factor(Pk$filename[Cd.NYCNOC]))
GNN1 <- ggplot(data=Pk[Cd.NYCNOC,], aes(x=freq_max_amp, y=bandwidth, color=filename)) +
  geom_point()  + ggtitle("LB vs. FME (NYCNOC? only)")
GNN2 <- ggplot(data=Pk[Cd.NYCNOC,], aes(x=duration, y=freq_min, color=filename)) +
  geom_point()  + ggtitle("FT vs. Durée (NYCNOC? only)")
ggarrange(GNN1, GNN2, common.legend = T, legend = 'none')

```



## Full table (any > Trsh)  

```{r 'Full table 05', eval=T, include=F, results='asis'}
op <- options(gvis.plot.tag='chart') ### to export the chart/table in knitted html
Table <- gvisTable(DT.RBC[,-c(1,3,4)])
plot(Table)


```


