---
title: "Output of Batclassify"
author: "JF Godeau"
date: "`r Sys.setlocale('LC_ALL', 'en_GB.UTF-8'); format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    fig_caption: yes
    self_contained: no
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
#FILE <- file.choose()
DIR <- "/media/jf/Elements/Audiomoth/20180713_AfterLIFE_Mellier/PAVONIA"
FILE <- paste(DIR,"Results.csv",sep="/")
require(data.table)
require(lubridate)
require(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
#knitr::opts_knit$set(root.dir=DIR) # ???
# Threshold value of probablilities to discard
Trsh <- 0.69
```

## General info

```{r 'Reformat Date and Time'}
RBC <- read.csv(FILE)
DT.RBC <- data.table(RBC)
DT.RBC[, Date := ymd(substring(DT.RBC$FileName,1,10))]
DT.RBC[, Time := as.character(hms(substring(DT.RBC$FileName,12,19)))]
PER <- max(ymd_hms(DT.RBC$FileName, tz="Europe/Amsterdam")) - min(ymd_hms(DT.RBC$FileName, tz="Europe/Amsterdam"))
PER.h <- round(difftime(max(ymd_hms(DT.RBC$FileName, tz="Europe/Amsterdam")),
                        min(ymd_hms(DT.RBC$FileName, tz="Europe/Amsterdam"))
                        ,units="hours"),1)
DT.num <- data.table(DT.RBC[,5:16], keep.rownames=T)
#DT.num[,Ppyg := NULL] ## !! Remove Ppyg data!!
LogiLine2keep <- apply(DT.num, 1, max) > Trsh
LogiLine2keepNoPyg <- apply(DT.num[,-10], 1, max) > Trsh

TM <- as.POSIXct(DT.RBC$FileName, format="%Y-%m-%d_%H_%M_%S")
TM.TSH <- data.frame(time=TM[LogiLine2keepNoPyg])
TM.TSH$valmax <- apply(DT.num, 1, max)[LogiLine2keepNoPyg]
require(ggplot2)
#ggplot(TM.TSH, aes(time, valmax)) + geom_point()
G1 <- ggplot(data.frame(TM), aes(TM, 0)) +
  geom_point() +
  theme_bw()+
  #  geom_point(data=TM.TSH, aes(time, valmax), col="red",  inherit.aes = F) +
  #  scale_y_continuous(limits=c(min(TM.TSH$valmax), max(TM.TSH$valmax))) +
  geom_histogram(data=TM.TSH, aes(x=time), stat ="bin",  inherit.aes = F, alpha= 0.5, binwidth=1000) +
  #  scale_y_continuous(sec.axis = sec_axis(~., name = "NEW")) +
  scale_x_datetime(date_breaks="2 hours") +
  theme(axis.text.x = element_text(angle = 90, vjust = 1.0, hjust = 1.0))+
  xlab("Time") + ylab("N samples > Threshold")

```

Name of the folder: **`r unique(DT.RBC$FilePath)`**  
Number of files: **`r dim(DT.RBC)[1]`**  
Number of files with at least one probability value above the threshold (defined as `r Trsh`): **`r sum(LogiLine2keep)`**  
Dates recorded for these files: `r paste(unique(DT.RBC$Date), collapse="; ")`  
Time difference between first and last recording: **`r round(PER,1)`** , (= `r PER.h` hours).  

## Distribution of the data in time  
Black dots at y=0 shows the recording period.  

```{r, fig.height=3}
G1
```

## Maximal score obtained for each species
### All species of Batclassify result table

```{r "Global probability for each species"}
MxSp <- sapply(DT.num, max)
#kable(MxSp, caption="General score")
kable(data.frame(t(MxSp)), caption="General score")
```

### Only species with a probability above the threshold (`r Trsh`)  

```{r "Global probability for each species Sup threshold"}
kable(data.frame(t(MxSp[MxSp > Trsh])), caption="Species with p > 0.5")
```

## Number of files where probability is at least above the threshold
### For each species  

```{r 'Select the species, if any, above the threshold for each file'}
CompMax <- cbind(max.col(DT.num[LogiLine2keep,], "first"),
                 max.col(DT.num[LogiLine2keep,], "last"))
Follow <- apply(DT.num[LogiLine2keep,] ,
                1,
                function(x){ord <- order(x, decreasing = T)
                paste(paste(colnames(DT.num)[ord][ x[ord] > Trsh][-1],
                            x[ord][ x[ord] > Trsh][-1]), collapse=" / ")
                })
LogiOneMax <- CompMax[,1] - CompMax[,2] == 0
DFSpMax <- cbind(FileName=as.character(DT.RBC$FileName[LogiLine2keep]),
                 SpeciesMax=names(DT.num)[CompMax[,1]],
                 Prob=apply(DT.num, 1, max)[LogiLine2keep],
                 OtherSp = as.character(Follow))

if(any(!LogiOneMax)){
  Idx <- which(!LogiOneMax)
  if(sum(!LogiOneMax)>1){
    DFSpMax[Idx,2] <- apply(matrix(names(DT.num)[CompMax],
                                   nrow=length(LogiOneMax))[Idx,],
                            1,
                            function(x) paste(x, collapse="-"))
  } else {
    DFSpMax[Idx,2] <- paste(names(DT.num)[CompMax[Idx,]], collapse = "-")
  }
}
DFSpMax <- data.frame(DFSpMax)

kable(sort(table(DFSpMax$SpeciesMax), decreasing = T), col.names = c("Species","N"))
```

### For each species per category of probability  

```{r SepProbCat}
kable(as.data.frame.matrix(table(DFSpMax$SpeciesMax, round(as.numeric(as.character(DFSpMax$Prob)),1))),
      caption="Number of files with each species for probablility categories")
```

## Fully detailed results (raw)

```{r 'Final table (PDF or docx)', include=F}
kable(DFSpMax) #If not html output
```


```{r 'Final table', eval=T, include=T, results='asis'}
suppressPackageStartupMessages(library(googleVis))
require(googleVis)
op <- options(gvis.plot.tag='chart') ### to export the chart/table in knitted html
Table <- gvisTable(DFSpMax,
                   options=list(page='enable',pageSize=20))
plot(Table)
```

## Analyse of NSL group

```{r "NSL-metrics"}
require(bioacoustics)
require(ggpubr)
Nms <- DFSpMax$FileName[grepl("NSL", DFSpMax$SpeciesMax) | grepl("NSL", DFSpMax$OtherSp)]
Pktmp <- do.call("rbind",
                 lapply(Nms, function(x){
                   AUD <- read_audio(paste0(DIR,"/",x,".wav"))
                   Output <- try(threshold_detection(AUD,
                                                     settings=T, HPF=17000,
                                                     FFT_size = 1024, threshold = 4))
                   Output$event_data[,c("filename", "starting_time", "duration",
                                        "freq_max_amp", "freq_max", "freq_min",
                                        "bandwidth", "slope", "curve_neg", "snr")]
                 }))
Pk <- droplevels(Pktmp[Pktmp$filename %in% names(which(table(Pktmp$filename) > 2)),])

## Logicals
Cd.NYCNOC <- Pk$freq_max_amp < 22000 & Pk$freq_min < 21000
Cd.QFC <- Pk$duration > 5 & Pk$bandwidth < 5000

DF.NSL <- data.frame(filename=names(table(Pk$filename)),
                     N.Signals = as.vector(table(Pk$filename)),
                     N.Sig_QFC = as.vector(table(Pk$filename[Cd.QFC])),
                     N.Sig_NYCNOC = as.vector(table(Pk$filename[Cd.NYCNOC])))
#kable(DF.NSL[order(DF.NSL$N.Signals.Freq, decreasing = T),])

```

The samples evaluated with at least 70% of probablility of belonging to the *NSL group* are analyzed with `bioacoustics::threshold_detection()`.  
First of all, we discard the recordings where less than 3 signals were detected (at the selected threshold!). The next graphs are finally performed on `r length(levels(Pk$filename))` files are selected out of `r length(unique(Nms))` files selected from BatClassify, totalizing `r dim(Pk)[1]` signals.  

### Full dataset of NSL
#### Dispersion on the FME and FT scale.  

```{r "NSL-plot1"}
bk.FME <- c(15,20,25,30,38,40,45,50)*1000
if(length(Pk[,1]) > 0){
  theme_set(theme_bw())
  ## Plots
  Gx1 <- ggplot(Pk, aes(y=freq_max_amp, x=factor(1))) +
    geom_boxplot() + geom_jitter(aes(color=filename), alpha = 0.3, size = 0.7) +
    ggtitle("FME (limit Nnoc ~ 22 kHz)") +
    geom_hline(yintercept = 22000, color='red', linetype=2) +
    xlab("") + scale_y_continuous(breaks = bk.FME)
  
  Gx2 <- ggplot(Pk, aes(y=freq_min, x=factor(1))) +
    geom_boxplot() + geom_jitter(aes(color=filename), alpha = 0.3, size = 0.7) +
    ggtitle("FT (limit Nnoc ~ 21 kHz)") +
    geom_hline(yintercept = 21000, color='orange', linetype=2) +
    xlab("") + scale_y_continuous(breaks = bk.FME)
  ggarrange(Gx1, Gx2, legend = 'none')
}
```

#### Plots *Barataud*

```{r "NSL-plot2"}
if(length(Pk[,1]) > 0){
  G1 <- ggplot(data=Pk, aes(x=freq_max_amp, y=bandwidth, color=filename)) +
    geom_point(size = 0.6) + ggtitle("LB vs. FME")
  G2 <- ggplot(data=Pk, aes(x=duration, y=freq_min, color=filename)) +
    geom_point(size = 0.6) + ggtitle("FT vs. Durée")
  ggarrange(G1, G2, common.legend = T, legend = 'none')
}
```

### Selection of possible QFC
At least 1 signal where duration > 5 ms and LB < 5 kHz.  

```{r "NSL-plot3"}
if(length(Pk[,1]) > 0){
  qfc.y1 <- c(0,6000)
  qfc.x1 <- c(15000,36000)
  qfc.y2 <- c(15000,36000)
  qfc.x2 <- c(5,26)
  if(any(Cd.QFC)){
    hist(table(Pk$filename[Cd.QFC]), 25,
         main="Frequency of presence of recordings (with min 3 signals/rec.)",
         xlab="Number of signals per file")
    
    Gqfc1 <- ggplot(data=Pk[Cd.QFC,], aes(x=freq_max_amp, y=bandwidth, color=filename)) +
      geom_point(size = 0.6)  + ggtitle("LB vs. FME (QFC only!)") + ylim(qfc.y1) + xlim(qfc.x1)
    Gqfc2 <- ggplot(data=Pk[Cd.QFC,], aes(x=duration, y=freq_min, color=filename)) +
      geom_point(size = 0.6)  + ggtitle("FT vs. Durée (QFC only!)") + ylim(qfc.y2) + xlim(qfc.x2)
    ggarrange(Gqfc1, Gqfc2, common.legend = T, legend = 'none')
  }
}
```

### Selection of possible *Nyctalus noctula*
i. e. FME < 22 kHz and FT < 21 kHz

```{r "NSL-plot4"}
if(any(Cd.NYCNOC)){
  #  table(factor(Pk$filename[Cd.NYCNOC]))
  hist(table(Pk$filename[Cd.NYCNOC]), 25,
       main="Frequency of presence of recordings (with min 3 signals/rec.)",
       xlab="Number of signals per file")
  
  GNN1 <- ggplot(data=Pk[Cd.NYCNOC,], aes(x=freq_max_amp, y=bandwidth, color=filename)) +
    geom_point(size = 0.6)  + ggtitle("LB vs. FME (NYCNOC? only)")
  GNN2 <- ggplot(data=Pk[Cd.NYCNOC,], aes(x=duration, y=freq_min, color=filename)) +
    geom_point(size = 0.6)  + ggtitle("FT vs. Durée (NYCNOC? only)")
  ggarrange(GNN1, GNN2, common.legend = T, legend = 'none')
}
```

### Recap per file  

```{r 'NSL table', eval=T, include=T, results='asis'}
op <- options(gvis.plot.tag='chart') ### to export the chart/table in knitted html
Table <- gvisTable(DF.NSL[order(DF.NSL$N.Signals, decreasing = T),],
                   options=list(page='enable',pageSize=25))
plot(Table)
```

## Analyse of Ppyg group
Valeurs moyennes des métriques sur tous les signaux par fichier.  

```{r "Ppyg-metrics"}
Nms <- DFSpMax$FileName[grepl("Ppyg", DFSpMax$SpeciesMax)]
if(length(Nms) > 0){
  Pk.Ppgtmp <- do.call("rbind",
                       lapply(Nms, function(x){
                         AUD <- read_audio(paste0(DIR,"/",x,".wav"))
                         Output <- try(threshold_detection(AUD,
                                                           settings=T, HPF=17000,
                                                           FFT_size = 1024, threshold = 4))
                         Output$event_data[,c("filename", "starting_time", "duration",
                                              "freq_max_amp", "freq_max", "freq_min",
                                              "bandwidth", "slope", "curve_neg", "snr")]
                       }))
  if(length(Pk.Ppgtmp) != 0){
    Pk.Ppg <- droplevels(Pk.Ppgtmp[Pk.Ppgtmp$filename %in% names(which(table(Pk.Ppgtmp$filename) > 2)),])
  } else {Pk.Ppg <- NULL}
  
  ## Logicals
  if(length(Pk.Ppg[,1]) > 0){
    Cd.QFC <- Pk.Ppg$duration > 5 & Pk.Ppg$bandwidth < 5000
    DF.Ppg <- data.frame(N.Signals = as.vector(table(factor(Pk.Ppg$filename))),
                         #           N.Sig_QFC = as.vector(table(Pk.Ppg$filename[Cd.QFC])),
                         FME = tapply(Pk.Ppg$freq_max_amp, Pk.Ppg$filename, median),
                         FT = tapply(Pk.Ppg$freq_min, Pk.Ppg$filename, median))
    #kable(DF.Ppg[order(DF.Ppg$N.Signals.Freq, decreasing = T),], row.names = F, caption = "Valeurs moyennes des métriques sur tous les signaux par fichier")
  } else {DF.Ppg <- data.frame(N.Signals = NA, FME = NA, FT = NA)}
}
```

The samples evaluated with at least 70% of probablility of belonging to the *Ppyg group*, at the first place, are presented. The measures performed by threshold_detection() function were done with the parameters FFT_size = 1024 and threshold = 4.  
First of all, we discard the recordings where less than 3 signals were detected (at the selected threshold!). The next graphs are finally performed on `r length(levels(Pk.Ppg$filename))` files are selected out of `r length(unique(Nms))` files selected from BatClassify, totalizing `r dim(Pk.Ppg)[1]` signals.  

### Full dataset of Ppyg
#### Dispersion on the FME and FT scale.  

```{r "Ppyg-plot1"}
if(length(Pk.Ppg[,1]) > 0){
  theme_set(theme_bw())
  ## Plots
  Gx1 <- ggplot(Pk.Ppg, aes(y=freq_max_amp, x=factor(1))) +
    geom_boxplot(size = 0.6) + geom_jitter(aes(color=filename), alpha = 0.5) +
    ggtitle("FME") +
    xlab("") + scale_y_continuous(breaks = bk.FME)
  Gx2 <- ggplot(Pk.Ppg, aes(y=freq_min, x=factor(1))) +
    geom_boxplot(size = 0.6) + geom_jitter(aes(color=filename), alpha = 0.5) +
    ggtitle("FT") +
    xlab("") + scale_y_continuous(breaks = bk.FME)
  ggarrange(Gx1, Gx2, legend = 'none')
}
```

#### Plot *Barataud*  

```{r "Ppyg-plot2"}
if(length(Pk.Ppg[,1]) > 0){
  Gqfc1 <- ggplot(data=Pk.Ppg, aes(x=freq_max_amp, y=bandwidth, color=filename)) +
    geom_point(size = 0.6)  + ggtitle("LB vs. FME")
  Gqfc2 <- ggplot(data=Pk.Ppg, aes(x=duration, y=freq_min, color=filename)) +
    geom_point(size = 0.6)  + ggtitle("FT vs. Durée")
  ggarrange(Gqfc1, Gqfc2, common.legend = T, legend = 'none')
}
```


```{r 'Ppyg table', eval=T, include=T, results='asis'}
if(length(Pk.Ppg[,1]) > 0){
  op <- options(gvis.plot.tag='chart') ### to export the chart/table in knitted html
  Table <- gvisTable(Pk.Ppg,
                     options=list(page='enable',pageSize=25))
  plot(Table)
}
```


## Analyse of Ppip group
Valeurs moyennes des métriques sur tous les signaux par fichier.  

```{r "Ppip-metrics"}
Nms <- DFSpMax$FileName[grepl("Ppip", DFSpMax$SpeciesMax)]
if(length(Nms) > 0){
  Pk.Piptmp <- do.call("rbind",
                       lapply(Nms, function(x){
                         AUD <- read_audio(paste0(DIR,"/",x,".wav"))
                         Output <- try(threshold_detection(AUD,
                                                           settings=T, HPF=17000,
                                                           FFT_size = 1024, threshold = 4))
                         Output$event_data[,c("filename", "starting_time", "duration",
                                              "freq_max_amp", "freq_max", "freq_min",
                                              "bandwidth", "slope", "curve_neg", "snr")]
                       }))
  Pk.Pip <- droplevels(Pk.Piptmp[Pk.Piptmp$filename %in% names(which(table(Pk.Piptmp$filename) > 2)) , ])
  ## Logical
  Cd.QFC <- Pk.Pip$duration > 5 & Pk.Pip$bandwidth < 5000
  
  DF.Pip <- data.frame(filename=names(table(Pk.Pip$filename)),
                       N.Signals = as.vector(table(factor(Pk.Pip$filename))),
                       N.Sig_QFC = as.vector(table(Pk.Pip$filename[Cd.QFC])),
                       FME = round(as.vector(tapply(Pk.Pip$freq_max_amp, Pk.Pip$filename, median))/1000 , 2),
                       FT = round(as.vector(tapply(Pk.Pip$freq_min, Pk.Pip$filename, median))/1000 , 2)
  )
  #kable(DF.Pip[order(DF.Pip$N.Signals, decreasing = T),], row.names = F, caption = "Valeurs moyennes des métriques sur tous les signaux par fichier")
} # close if() line 350
```

The samples evaluated with at least 70% of probablility of belonging to *Ppip*, at the first place, are presented. The measures performed by threshold_detection() function were done with the parameters FFT_size = 1024 and threshold = 4.  
`r try(length(levels(Pk.Pip$filename)))` files are selected, totalizing `r try(dim(Pk.Pip)[1])` signals.  

### Full dataset of Ppip
#### Dispersion on the FME and FT scale.  

```{r "Ppip-plot1"}
if(length(Pk.Pip[,1]) > 0){
  theme_set(theme_bw())
  ## Plots
  Gx1 <- ggplot(Pk.Pip, aes(y=freq_max_amp, x=factor(1))) +
    geom_boxplot() + geom_jitter(aes(color=filename), alpha = 0.5, size=0.4) +
    ggtitle("FME") +
    xlab("") + geom_hline(yintercept =  43000) + scale_y_continuous(breaks = bk.FME) +
    ylim(c(30000,max(Pk.Pip$freq_max_amp)))
  Gx2 <- ggplot(Pk.Pip, aes(y=freq_min, x=factor(1))) +
    geom_boxplot() + geom_jitter(aes(color=filename), alpha = 0.5, size=0.4) +
    ggtitle("FT") +
    xlab("") + geom_hline(yintercept =  42000) + scale_y_continuous(breaks = bk.FME) +
    ylim(c(30000,max(Pk.Pip$freq_min)))
  ggarrange(Gx1, Gx2, legend = 'none')
}
```

#### Plot Barataud  
**No QFC!**  

```{r "Ppip-plot2"}
if(length(Pk.Pip[,1]) > 0){
  #  table(factor(Pk.Pip$filename))
  NmsPipSp <- DF.Pip$filename[DF.Pip$FME < 43 & DF.Pip$FME > 32]
  Pk.Pip$Med38 <- "Ppip"
  Pk.Pip$Med38[Pk.Pip$filename %in% NmsPipSp] <- "PipNat?"
  Gqfc1 <- ggplot(data=Pk.Pip[Pk.Pip$bandwidth > 5000,], aes(x=freq_max_amp, y=bandwidth, color=Med38)) +
    geom_point(size=0.4)  + ggtitle("FMAppl: LB vs. FME") + xlim(c(32000, 70000))
  Gqfc2 <- ggplot(data=Pk.Pip[Pk.Pip$bandwidth > 5000,], aes(x=duration, y=freq_min, color=Med38)) +
    geom_point(size=0.4)  + ggtitle("FMAppl: FT vs. Durée") + ylim(c(30000,65000))
  ggarrange(Gqfc1, Gqfc2, common.legend = T)
}
```

#### QFC: PIPPIP

```{r "Ppip-plot3", warning=F}
qfc.y1 <- c(-2000,6000)
qfc.x1 <- c(30000,60000)
qfc.y2 <- c(30000,60000)
qfc.x2 <- c(5,17)

if(length(Pk.Pip[,1]) > 0){
  #  table(factor(Pk.Pip$filename[Cd.QFC]))
  NmsPipSpQFC <- DF.Pip$filename[DF.Pip$FME < 41 & DF.Pip$FME > 30]
  Pk.Pip$Med38[Pk.Pip$filename %in% NmsPipSpQFC] <- "PipNat?"
  Gqfc1 <- ggplot(data=Pk.Pip[Cd.QFC,], aes(x=freq_max_amp, y=bandwidth, color=Med38)) +
    geom_point(size = 0.5) +
    ggtitle("LB vs. FME (QFC only!)") +
    ylim(qfc.y1) + xlim(c(30000,60000))
  Gqfc2 <- ggplot(data=Pk.Pip[Cd.QFC,], aes(x=duration, y=freq_min, color=Med38)) +
    geom_point(size = 0.5) +
    ggtitle("FT vs. Durée (QFC only!)") +
    ylim(c(30000,55000)) + xlim(c(5,17))
  ggarrange(Gqfc1, Gqfc2, common.legend = T)
}

```

#### Main table per recording

```{r 'Ppip table', eval=T, include=T, results='asis'}
if(length(Pk.Pip[,1]) > 0){
  op <- options(gvis.plot.tag='chart') ### to export the chart/table in knitted html
  Table <- gvisTable(as.data.frame(DF.Pip[order(DF.Pip$N.Signals, decreasing = T),]),
                     options=list(page='enable',pageSize=25))
  plot(Table)
}
```

## Detailed results with additional info based on the results of bioacoustics analysis  
Exclusion of records with less than 3 signals detected.  

```{r}
if(exists("DF.NSL")){
  Nm.NSL <- stringr::str_sub(as.character(DF.NSL$filename), end=-5)
  NSL <- ifelse(DFSpMax$FileName %in% Nm.NSL, "NSL", "")} else {NSL <- rep("",length(DFSpMax$FileName))}

if(exists("DF.Ppg")){
  Nm.Pg <- stringr::str_sub(row.names(DF.Ppg), end=-5)
  Ppyg <- ifelse(DFSpMax$FileName %in% Nm.Pg, "Ppyg?", "")} else {Ppyg <- rep("",length(DFSpMax$FileName))}

if(exists("DF.Pip")){
  Nm.Pp <- stringr::str_sub(as.character(DF.Pip$filename), end=-5)
  Ppip <- ifelse(DFSpMax$FileName %in% Nm.Pp, "Ppip", "")
  Lg.Psp <- DFSpMax$FileName %in% stringr::str_sub(as.character(NmsPipSp), end=-5)
  Ppip[Lg.Psp] <- "PipNat?"
} else {
  Ppip <- rep("",length(DFSpMax$FileName))}

DFSpMax$Add <- paste(NSL, Ppyg, Ppip, sep = "-")
```

```{r 'Enriched table', eval=T, include=T, results='asis'}
op <- options(gvis.plot.tag='chart') ### to export the chart/table in knitted html
Table <- gvisTable(DFSpMax)
plot(Table)
```

